Estimating statical precison for parameters of Ecological Economics-inspired production functions

### 2015-10-02 Articles/Article_EcolEcon_2015/Paper0/Paper0-Resampling.Rnw
Rename Paper 0 folder to Paper0

@@

For this paper, we perform limited, but enlightening,
statistical resampling analyses
to provide an indication of the precision with which parameters are known.
(See Section~\ref{sec:resampling}.)
In a section on future work (see Section~\ref{sec:conclusionsFinal}),%
\authNote{This section number is incorrect. Why?}
we provide some suggestions for a way forward.

@@

%------------------------------
\subsubsection{Parameter precision}
\label{sec:resampling}
%------------------------------

>>>>

%------------------------------
\subsubsection{Constant Elasticity of Substitution Production Function (CES)} 
\label{sec:CES}
%------------------------------

The energy-augmented 
Constant Elasticity of Substitution (CES) production function%
  \footnote{
  We use the The \texttt{R} 
  % \citep{R} 
  package \texttt{micEconCES} 
  % \citep{Henningsen:2011td} 
  to estimate the CES production function.
  }
can be given as
%
\begin{equation} \label{eq:CESgeneric}
  y = \gamma \: A \: \left\{\delta \left[\delta_1 x_1^{-\rho_1} 
      + (1-\delta_1)x_2^{-\rho_1} \right]^{\rho/\rho_1} 
      + (1-\delta) x_3^{-\rho} \right\}^{-1/\rho}; 
      A \equiv \mathrm{e}^{\lambda (t-t_0)},
\end{equation}
%
where
$y \equiv Y/Y_{0}$,
$\gamma$ is a scale parameter,
e is the base of the natural logarithm, 
$\lambda$ is the Solow residual (often thougth to represent the pace of technological progress),
$t$ (time) is measured in years,
$x_1$, $x_2$, and $x_3$ are factors of production
and permutations of capital~($k$), labor~($l$), and energy~($e$),
$k \equiv K/K_{0}$, 
$l \equiv L/L_{0}$, 
$Y$ (economic output) is represented by GDP, 
$K$ (capital) is expressed in currency units, 
$L$ (labor) is expressed in workers or work-hours/year, and
the 0 subscript indicates values at an initial year.%
  \footnote{Dimensionless, indexed quantities are represented by 
  lower-case symbols 
  ($y$, $k$, $l$, $e$, $q$, $x$, and $u$), and dimensional 
  quantities are represented by upper-case symbols 
  ($Y$, $K$, $L$, $E$, $Q$, $X$, and $U$). 
  Model parameters are represented by Greek letters
  ($\alpha_1$, $\alpha_2$, $\lambda$, $\theta$).
  }
The CES model without energy is given in Equation~\ref{eq:CESkl}.
%
\begin{equation} \label{eq:CESkl}
  y = \gamma \: A \: \left[\delta_1 k^{-\rho_1} 
      + (1-\delta_1)l^{-\rho_1} \right]^{-1/\rho_1}; 
      A \equiv \mathrm{e}^{\lambda (t-t_0)} . 
\end{equation}
%
Equation~\ref{eq:CESkle} augments Equation~\ref{eq:CESkl} with energy 
using a ($kl$)($e$) nesting structure, as is typical in the literature. 
Equation~\ref{eq:CESkl} is a degenerate form of Equation~\ref{eq:CESkle} 
where $\delta \rightarrow 1$. 
%
\begin{equation} \label{eq:CESkle}
  y = \gamma \: A \: \left\{\delta \left[\delta_1 k^{-\rho_1} 
      + (1-\delta_1)l^{-\rho_1} \right]^{\rho/\rho_1} 
      + (1-\delta) e^{-\rho} \right\}^{-1/\rho}; 
      A \equiv \mathrm{e}^{\lambda (t-t_0)}.
\end{equation}
%
In the CES production function, 
$\gamma$ is a fitting parameter that accounts for an atypical first year. 
The fitting parameters $\rho_1$ and $\rho$ indicate elasticities 
of substitution ($\sigma_1$ and $\sigma$).
The elasticity of substitution 
between capital ($k$) and labor ($l$) is given by 
$\sigma_1 = \frac{1}{1+\rho_1}$, and
the elasticity of substitution between ($kl$) and ($e$) is given by 
$\sigma = \frac{1}{1+\rho}$. 
As $\rho_1 \rightarrow 0$, $\sigma_1 \rightarrow 1$,
and the embedded CES production function for $k$ and $l$ degenerates 
to the Cobb-Douglas production function.
Similarly, as $\rho \rightarrow 0$, $\sigma \rightarrow 1$,
and the CES production function for $(kl)$ and $(e)$ degenerates 
to the Cobb-Douglas production function.
As $\sigma \rightarrow \infty$ ($\rho \rightarrow -1$), 
($kl$) and ($e$) are perfect substitutes. 
As $\sigma \rightarrow 0$ ($\rho \rightarrow \infty$), 
($kl$) and ($e$) are perfect complements: 
no substitution is possible. Similarly, 
as $\sigma_1 \rightarrow 0$ ($\rho_1 \rightarrow \infty$),
$k$ and $l$ are perfect complements.
$\delta_1$ describes the relative importance of capital ($k$)
and labor ($l$), and
$\delta$ describes the importance of ($kl$) relative to ($e$).

@@

@@
